### 2007-12-16 pr/Paper/Solution.tex
git-svn-id: https://forge.caliper.pl/scm/svn/private-memfis@589 14f08429-6e20-0410-a26c-ef81b9fd1c62

\section{Rozwi¹zanie rzeczywistego problemu}
\subsection{Struktura rozwi¹zania}

\begin{figure}[h!]
\centering
\includegraphics[width=8cm, trim=0 0 0 0, clip]{SolutionProcessors}
\caption{Procesory wykorzystywane podczas wykonywania pomiarów}
\label{fig:SolutionProcessors}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=8cm, trim=0 0 0 0, clip]{SolutionProcesses}
\caption{Procesory wykorzystywane podczas wykonywania pomiarów}
\label{fig:SolutionProcesses}
\end{figure}

\subsection{Wyniki rzeczywiste}